Thesis Title

### 2022-06-02 chapters/discussion.tex
Updates from Overleaf

\subsection{Limitation to the application of metagenomics in clinical microbiology}

\subsubsection{Limitations of sequencing technologies}

@@

\subsubsection{Limitations of host sequence contamination}

@@

\subsubsection{Limitations of the bioinformatic analysis}

@@

\subsection{Better standards in metagenomics for clinical microbiology}

\subsubsection{The need for better assessment}

@@

\paragraph{Performing proper benchmarking of software} \mbox{}\\

@@

\paragraph{The use of mock communities} \mbox{}\\

@@

\subsubsection{Ensuring reproducibility}

@@

\subsubsection{The need for intuitive and responsive reports}

\subsubsection{The adoption of standard specifications}

\subsubsection{Crowdsourcing for better standards}

>>>>

\section{Limitation to the application of metagenomics in clinical microbiology}

\subsection{Limitations of sequencing technologies}

@@

\subsection{Limitations of host sequence contamination}

@@

\subsection{Limitations of the bioinformatic analysis}

@@

\section{Better standards in metagenomics for clinical microbiology}

\subsection{The need for better assessment}

@@

\subsubsection{Performing proper benchmarking of software}

@@

\subsubsection{The use of mock communities}

@@

\subsection{The need for better reproducibility}

@@

\subsubsection{The need for Container Software}

\subsubsection{The need for Workflow managers}

\subsubsection{The need for Version Control}

\subsubsection{The need for Open Integration testing }

\subsection{The need for better Interpretability}

\subsection{The need for better Interoperability}

\subsection{The need for Crowdsourcing}
